%_________________________________________________________________________________________
%  Resume for Nathan McCandlish
\documentclass[]{resume}

\usepackage[letterpaper, top=1in,left=0.80in,right=2.1in,bottom=0.5in]{geometry}
\usepackage{comment}
\usepackage{xhfill}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{color}
\usepackage{transparent}
\urlstyle{same}
%  Formatting Commands

\renewcommand{\familydefault}{lmss}


%\addtolength{\voffset}{1em}

\setlength{\sectionskip}{1.8em}
\setlength{\parskip}{0.95em}
\linespread{1.20}

\renewcommand{\namefont}{}
\renewcommand{\sectionfont}{\bf \Large}
\newcommand\tab[1][.5cm]{\hspace*{#1}}


%__________________________________________________________________________________________
\begin{document}
\name{
\begin{tabular}{@{}p{8cm}p{8cm}}
\multirow{ 2}{*}{\huge \textbf {Nathan McCandlish}} & \hfill nsmccandlish@gmail.com\\
& \hfill linkedin.com/in/nsmccandlish\\
\large{Senior Software Engineer}
\end{tabular}
}
\begin{resume}
%%%%%
%\section{Contact}
%%%%%
\setlength{\sectionskip}{1.30em}
\section{SUMMARY\makebox[387 px]{\rule[.5 ex]{387 px}{1.0pt}}}
Pragmatic full stack engineer and mentor with 8 years experience championing best practices and guiding teams to deliver robust solutions. 
%%%%%
%\section{Skills}
%%%%%
\section{SKILLS\makebox[416 px]{\rule[.5 ex]{416 px}{1.0pt}}}
\vspace{0.9mm}
%%%%
\textbf{Languages:} \hspace*{11.5mm}
Python, Postgres, Typescript, React, GraphQL, Javascript, Bash \\
% sneaky keywords for ATS on things that are implied by my other listed skills?
% HTML, CSS? maybe implied with React. are JSON, YAML, XML languages? hahaha
% No Perl, that's a red flag
% 
\textbf{Tools/Frameworks:} SQLAlchemy, AWS, Pytest, Git, Github, Kubernetes, Docker, Jira, Django, \\
\hspace*{32mm}Celery, nginx, Redis, Linux, CircleCI, Jenkins, Github Actions, Jest, REST
% {\fontsize{0.1}{0.1}\selectfont \texttransparent{1}{ Pyramid, RabbitMQ, React Hooks, Ansible }}
%%%%%
\section{EXPERIENCE\makebox[372 px]{\rule[.5 ex]{372 px}{1.0pt}}}
%%%%% Juniper Square

\vspace{0.9mm}
\textbf{\large Juniper Square}\\
\tab \textbf{\textit{Senior Software Engineer}} \hfill \textit{Apr 2020 - Feb 2023}
\begin{itemize}
    \item
    Spearheaded delivery of key engineering projects including asset reporting, Looker \\
    integration, Outlook add-in, and customizable SSO integration. Partnered cross-functionally \\
    with QA, product, design, and CS to understand requirements and promote smooth delivery.
    % Autoformatter (black/isort) implementation - shouldn't have even been a big project in 2020, skip
    % can I give metrics here? Didn't save real ones with numbers :(
    %.     - Salespeople use asset reporting for demos because it's so polished, even if it's not relevant to the customer lol
    %.     - analytics integration was the "smoothest project JSQ has ever had" -Xanthe (first project I solo led :100:)
    %      - A top emoji-replier in slack, drove engagement by making custom emoji
    \item
    Enabled critical functionality for major customers by resolving complex database performance \\
    issues through query optimization and efficient caching, improving speeds by over 50x.
    \item
    Coordinated upgrades to Python 3.8 and Postgres 14, and decreased CI times by 70\%+.
     % this bullet has way too many words, but I'm fighting to stay in a single page
     % perf improvements - maybe remove?
     % zero-downtime vs rolling/downgradeable deployments, focus on DB schema consolidation project
     % 
    \item
    Provided technical leadership and mentoring across fast-growing engineering team. \\
    Empowered colleagues to overcome obstacles through diligent architecture and code reviews \\
    focused on improving overall quality, test coverage, and adherence to best practices.
    % Cross-environment DB schema consolidation project - how do I succinctly describe this in a way that it's meaningful?
   % Anything to include here about strong relationships with PMs? Breaking projects into chunks?
   % Moved us from project-branches towards culture feature flags and merging straight to dev
   % "Be the change you want to see" -> Have an idea for a process change, make it happen for a project, show the org why it worked well
\end{itemize}

%%%%% Aperio Group

\vspace{0.9mm}
\textbf{\large Aperio Group} {\textit{\large(acquired by BlackRock)}}\\
\tab \textbf{\textit{Senior Full-Stack Software Engineer}} \hfill \textit{June 2018 - Apr 2020}
\begin{itemize}
    \item
    Collaborated with Portfolio Management and Research teams to build and implement \\
    project requirements for Aperio\textsc{\char13}s proprietary trading platform.
    \item
    Served as lead engineer for project of storing, processing, and optimizing portfolios using \\
    a new ESG (Environmental, Social, Governance) investing data source.
    \item
    Proposed and lead improvements for engineering standards, tooling, and processes.
\end{itemize}

%%%%% Bizowie

\textbf{\large Bizowie Cloud ERP}\\
\tab\textbf{\textit{Software Developer}} \hfill \textit{Mar 2015 - June 2018}
\begin{itemize}
    \item
    Gathered requirements and developed functionality for areas of business including \\
    accounting, CRM, inventory management, pricing, purchasing, AP/AR, and manufacturing.
    \item
    Designed and implemented modular data import system, reducing development \\
    time to onboard new clients from days to minutes.
    \item 
    Quickly identified and resolved production issues e.g.\ bugs, deadlocks, and failing messages.
\end{itemize}


%%%%%
\section{EDUCATION\makebox[372 px]{\rule[.5 ex]{372 px}{1.0pt}}}
\vspace{0.9mm}
%%%%%
\textbf{\large The University of Pittsburgh} \hfill \textit{Apr 2014}\vspace{0.7mm}\\ 
\hspace*{4mm}Bachelor of Science \emph{summa cum laude} in Mathematics, Minor in Economics\\ % indent this?
%\hspace*{16mm}GPA: 3.86
%\textbf{Culver Award}  - University of Pittsburgh Mathematics Department  \hfill \textit{Apr 2014}\vspace{0.7mm}
\clearpage
\end{resume}
\end{document}%